\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.4in,top=0.4in,right=0.40in,bottom=0.5in]{geometry} % Document margins
\usepackage{hyperref}

%Document line spacing
\usepackage{setspace}

\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}

\name{Logan Ge} % Your name
% You can merge both of these into a single line, if you do not have a website.
\address{+1(312) 826-9860 \\ Chicago, IL \\ gelogan@uchicago.edu \\ \href{http://github.com/geloganu}{github.com/geloganu}}

\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------
\vspace{-0.6em}
\begin{rSection}{Education}
{\bf University of Chicago}\hfill {Expected Jun, 2023}\\
B.A. in Physics, Honors $|$ Major GPA 3.84/4.00 $|$ Cumulative GPA 3.74/4.00
\smallskip\\
\textbf{Relevant Coursework}: Machine Learning, Statistical Models \& Methods, Computational Physics, Abstract Linear Algebra, Adv. Quantum Mechanics, Statistical Physics, Solid State Physics, Quantitative Portfolio Management \& Algorithmic Trading.\smallskip\\
\textbf{Honors Thesis}: Numerical Exact Diagonalization and Entanglement Spectrum Study of the $\nu = 5/2$ State under Gaussian Background Disorder (supervised by Prof. Woowon Kang).


\end{rSection}

%----------------------------------------------------------------------------------------
% Work experience
%----------------------------------------------------------------------------------------
\vspace{-0.5em}
\begin{rSection}{EXPERIENCE}

\textbf{Kang Group at the University of Chicago} \hfill October 2021 - Present\\
\textit{Computational Research Assistant} \hfill \textit{Chicago, IL}
\vspace{-0.6em}
 \begin{itemize}
   \itemsep -5.8pt {}
   \item Developed and deployed scientific simulation program to model quantum Hall condensed matter systems, utilizing state-of-the-art exact diagonalization techniques and algorithms in Python and Julia, adopted as lab group simulation method. 
   \item Integrated multicore parallel computing capabilities through Linux bash scripting, increasing simulation speed by 150\%.
   \item Implemented standardized data visualization templates for energy and entanglement spectrums graphs for lab group.
   \item Collaborated with a cross-functional team of researchers, including faculty, and delivered project-specific functionality. 
\end{itemize}


\textbf{James Franck Institute} \hfill June 2022  - September 2022 \\
\textit{Summer Undergraduate Researcher} \hfill \textit{Chicago, IL}
\vspace{-0.6em}
 \begin{itemize}
   \itemsep -5.8pt {}
   \item Overhauled outdated programs from Fortran to Python and implemented numerical modeling pipeline that consolidated data generation, preprocessing, and modeling, streamlining experimental trials and data analysis times by up to 40\%.
   \item Configured efficient experimental layout in collaboration with faculty and installed ultra-high vacuum and dilution fridge.
    
 \end{itemize}

 \textbf{S.Y. Industrial Designs} \hfill July 2021  - August 2021 \\
\textit{Product Development Intern} \hfill \textit{Vancouver, Canada (Remote)}
\vspace{-0.6em}
 \begin{itemize}
   \itemsep -5.8pt {}
   \item Conducted market research to identify consumer preferences and trends in China, Taiwan, and Japan to develop and launch a new product line of teaware across the three countries with a revenue of ~\$5 million USD within the first year.
   \item Identified and negotiated with more cost-efficient production sites for product packaging, facilitating cost savings of \$250K.
  
    
 \end{itemize}

\end{rSection} 

%----------------------------------------------------------------------------------------
%Project section
%----------------------------------------------------------------------------------------
\vspace{-0.5em}
\begin{rSection}{PROJECTS}
\vspace{-1.25em}

\item  \textbf{Neural Network-Based Disordered Phase Transition Detector} \hfill {April 2023 - May 2023}
\begin{itemize}
   \vspace{-0.6em}
   \itemsep -5.8pt {}
   \item Preprocessed and initialized model dataset for disordered pfaffian state simulating highly accurate experimental conditions.
   \item Training artificial neural network using TensorFlow/Keras to predict properties and phase transitions of topological states.
\end{itemize}

\item  \textbf{NBA Over/Under Prediction} \hfill {March 2023}
\begin{itemize}
   \vspace{-0.6em}
   \itemsep -5.8pt {}
   \item Developed a Python-based API scraping tool using Requests library for live/historical NBA statistics and bookkeeper odds.
   \item Implemented a data cleaning and preprocessing pipeline ensuring consistency of collected data into SQLite3 database.
   \item Trained deep neural network and random forest classifier to predict O/U outcomes, achieved 62\% with backtesting script. 
  
\end{itemize}

\item \textbf{Mean Variance Portfolio Management} \hfill August 2021
\begin{itemize}
   \vspace{-0.6em}
   \itemsep -5.8pt {}
   \item Spearheaded a team of 4 students to develop multifunctional portfolio management tool and analyze portfolio performance.
   \item Conducted portfolio analysis for risk management and asset allocation strategies with regression analysis and forecasting.
\end{itemize}

\end{rSection} 


%----------------------------------------------------------------------------------------
%Leadership
%----------------------------------------------------------------------------------------
\vspace{-0.5em}
\begin{rSection}{Leadership and PROFESSIONAL DEVELOPMENT} 
\vspace{-1.25em}
\item \textbf{Boston Consulting Group} \hfill March 2023 \\
\textit{Data Science \& Advanced Analytics Virtual Experience Participant at The Forage}
   \begin{itemize}
   \vspace{-0.6em}
   \itemsep -5.8pt {}
   \item Participated in BCG's simulated project at the Forage, identified key business insights for client needs through data analysis.
   \item Delivered forecast analysis with random forest model in Scikit-Learn, achieved 91\% accuracy in identifying churned users.

   \end{itemize}

\textbf{The Campanile Project} \hfill July 2020 - January 2022 \\
\textit{Board Member}
 \begin{itemize}
   \vspace{-0.6em}
   \itemsep -5.8pt {}
    \item Coordinated collaborative effort between six undergraduate students to create a volunteer platform resulting in increased accessibility of volunteer program outreach by ten folds at 75\% cost savings compared to the voluntourism industry.
    \item Conducted client outreach to identify hundreds of potential partner organizations and establish long term relationships.
    
 \end{itemize}

\end{rSection}
%----------------------------------------------------------------------------------------
%Skills Section
%----------------------------------------------------------------------------------------
\vspace{-0.5em}
\begin{rSection}{SKILLS}

    \begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
    Programming Languages  & Python, Fortran, Julia, R Studios, Linux, COMSOL   \\

    Technologies  &   SQLite, TensorFlow/Keras, Scikit-Learn, SciPy, Pandas/NumPy, Matplotlib, Git\\

    Interests & Electric Guitar, Skiing, F1, Chicago Bulls
    \end{tabular}\\
    \end{rSection}

\end{document}